### 2016-09-28 revision/conclusions.tex
Add references to NIPS 2016 papers

We have designed a scale-free algorithm based on \textsc{Follow The Regularizer
Leader}. Its regret is $O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} +
\min{\sqrt{T}, D} \max_{t=1,2,\dots,T} \|\ell_t\|_* \right)$ with respect to any
competitor $u \in K$, where $f$ is any non-negative $1$-strongly convex function
defined on $K$ and $D$ is the diameter of $K$. The result makes sense even when
the decision set $K$ is unbounded.

@@

Notice that with the regularizer $f(u) = \frac{1}{2}\|u\|_2^2$ the regret of
\textsc{SOLO FTRL} depends quadratically on the norm of the competitor
$\|u\|_2$. There exist non-scale-free algorithms \cite{McMahan-Streeter-2012,
McMahan-Abernethy-2013, Orabona-2013, McMahan-Orabona-2014, Orabona-2014} that
have only a $O(\|u\|_2 \sqrt{\log \|u\|_2})$ or $O(\|u\|_2 \log \|u\|_2)$
dependency.  These algorithms assume an a priori bound on the norm of the loss
vectors. It remains an open problem to design algorithms that have sub-quadratic
dependency on $\norm{u}_2$ and are adaptive to the scale of the loss vectors.

>>>>

We have designed a scale-free algorithm based on \textsc{Follow The Regularizer
Leader}. Its regret with respect to any competitor $u$ is
$$
O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2}
+ \min\{\sqrt{T}, D\} \max_{t=1,2,\dots,T} \|\ell_t\|_* \right) \; ,
$$
where $f$ is any non-negative $1$-strongly convex
function defined on the decision set and $D$ is the diameter of the decision
set. The result makes sense even when the decision set is unbounded.

@@

Notice that with the regularizer $f(u) = \frac{1}{2}\|u\|_2^2$ the regret of
\textsc{SOLO FTRL} depends quadratically on the norm of the competitor
$\|u\|_2$. There exist non-scale-free algorithms \cite{McMahan-Streeter-2012,
McMahan-Abernethy-2013, Orabona-2013, McMahan-Orabona-2014, Orabona-2014,
Orabona-Pal-2016} that have only a $O(\|u\|_2 \sqrt{\log \|u\|_2})$ or
$O(\|u\|_2 \log \|u\|_2)$ dependency.  These algorithms assume an a priori bound
on the norm of the loss vectors. Recently, an algorithm that adapts to norms of
loss vectors and has $O(\|u\|_2 \sqrt{\log \|u\|_2})$ dependency was
proposed~\cite{Cutkosky-Boahen-2016}. However, the trade-off between the
dependency on $\norm{u}_2$ and the adaptivity to the norms of the loss vectors
still remains to be explored.

### 2016-09-28 revision/introduction.tex
Add references to NIPS 2016 papers

Scale-free versions of \textsc{MD} include \textsc{AdaGrad
MD}~\cite{Duchi-Hazan-Singer-2011}. However, the AdaGrad MD algorithm has a
non-trivial regret bounds only when the Bregman divergence associated with the
regularizer is bounded. In particular, since a bound on the Bregman divergence
implies that the decision set is bounded, the regret bound for \textsc{AdaGrad
MD} and is vacuous for unbounded sets. In fact, as we show in
Section~\ref{subsection:mirror-descent-lower-bound}, \textsc{AdaGrad MD} and
similar algorithms based on \textsc{MD} incurs $\Omega(T)$ regret, in the worst
case, if the Bregman divergence is not bounded.

>>>>

Scale-free versions of \textsc{MD} include \textsc{AdaGrad
MD}~\cite{Duchi-Hazan-Singer-2011}. However, the \textsc{AdaGrad MD} algorithm
has a non-trivial regret bounds only when the Bregman divergence associated with
the regularizer is bounded. In particular, since a bound on the Bregman
divergence implies that the decision set is bounded, the regret bound for
\textsc{AdaGrad MD} is vacuous for unbounded sets. In fact, as we show in
Section~\ref{subsection:mirror-descent-lower-bound}, \textsc{AdaGrad MD} and
similar algorithms based on \textsc{MD} incurs $\Omega(T)$ regret, in the worst
case, if the Bregman divergence is not bounded.
